### 2018-07-13 paper/sphinxes.tex
Sphinxes: adds CreateReply, UseReply, CreateFwd

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
\NewAlgorithm{\AttachPayload}{\Sphinxes[AttachPayload]}
\NewAlgorithm{\Process}{\Sphinxes[Process]}

@@

  \item \(\AttachPayload\) attaches a payload to the header using the proper 
    keys.
    This is what Sphinx~\cite[\S 3.3]{Sphinx} calls a forward message.

  \item \(\Process\) is the algorithm for processing incoming messages, the 
    processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but uses a 
    different interface.
\end{itemize}

@@

@@

@@

\paragraph*{The \(\AttachPayload\) algorithm}

\paragraph*{The \(\Process\) algorithm}

>>>>

\NewScheme{\Sphinxes}{POR}
\NewAlgorithm{\CreateHeader}{\Sphinxes[CreateHeader]}
\NewAlgorithm{\CreateFwd}{\Sphinxes[CreateForward]}
\NewAlgorithm{\CreateReply}{\Sphinxes[CreateReply]}
\NewAlgorithm{\UseReply}{\Sphinxes[UseReply]}
\NewAlgorithm{\ProcessHeader}{\Sphinxes[ProcessHeader]}

@@

  \item \(\UseReply\) takes a reply header and attaches a message.

  \item \(\ProcessHeader\) is the algorithm for processing incoming messages, 
    the processing is identical to Sphinx~\cite[\S 3.6, \S 3.7]{Sphinx} but 
    uses a different interface.
\end{itemize}

@@

This algorithm computes a forward header with a message to be delivered to the 
destination.
It takes as input a sequence, \(L = \{L_0, \dotsc, L_\nu\}\), of node sets, 
such that \(\nu+1\leq r\) and \(L_\nu\) is either \(\{\nullnode\}\) or 
\(\{\rdvnode\}\), and a message \(m\).
(\Ie \(L_{\nu-1}\) is the final destination.)

It first runs \(\CreateHeader\) with \(I = 0_\kappa\) to compute a mix header 
\(M_0\) and the keys \(s_i\) for each layer \(i\).
Then, for \(\nu\leq i\leq 0\), it will compute
\begin{equation*}
  \delta_i = \prp\left(
    \hash_\prp\left(s_i\right),
    \delta_{i+1}\right),
\end{equation*}
where \(\delta_{\nu+1}\) is the message \(m\).

@@

This algorithm prepares a header that can be used for anonymous replies.
It takes as input a sequence, \(L = \{L_0, \dotsc, L_\nu\}\), of node sets, 
such that \(\nu+1\leq r\), \(L_\nu\) is either \(\{\nullnode\}\) or 
\(\{\rdvnode\}\) and \(L_{\nu-1}\) is the set of own addresses.

It first runs \(\CreateHeader\) with \(I\rgets \bin^\kappa\) to compute a mix 
header \(M_0\) and the keys \(s_i\) for each layer \(i\).
It chooses uniformly randomly a key \(\tilde k\rgets \bin^\kappa\).
Finally, it returns
\(I\),
the tuple of keys \((\tilde k, \hash_\prp(s_0), \dotsc, \hash_\prp(s_\nu))\),
and \((L_0, M_0, \tilde k)\).

The tuple of keys must be stored in a local table indexed by \(I\).
The tuple \((L_0, M_0, \tilde k)\) should be given to the sender who wants to 
use the anonymous reply.

\paragraph*{The \(\UseReply\) algorithm}

This algorithm takes a reply header \((L_0, M_0, \tilde k)\) and a message 
\(m\) as input.
It then returns \((M_0, \prp(\tilde k, m))\) which should be sent to any node 
in \(L_0\).

\paragraph*{The \(\ProcessHeader\) algorithm}

@@
